---
title: "Application of the GOF procedures for compound distribution on real insurance data set"
output: html_notebook
author: Pierre-O Goffard
---
The inference and goodness-of-fit techniques developped in the FTCD package
```{r, echo = FALSE, message = FALSE, include = FALSE, warning = FALSE}
library(FTCD)
library(tidyverse)
library(fitdistrplus)
library(moments)
library(xtable)
library(e1071)
library(tea)
library(expint)
library(actuar)
library(ggplot2)
options(warn=-1)
export_path <- "C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/"
```
are illustrated on an actuarial data set `itamtpltcost` accessible from the package `CASdatasets`.
```{r, message = FALSE, echo = FALSE, warning = FALSE}
library(sp)
library(xts)
#install.packages("CASdatasets", repos = "http://dutangc.free.fr/pub/RRepos/", type="source")
library(CASdatasets)
data(itamtplcost)
```
This dataset contains losses (in excess of $500,000$ euros) of an italian third-party liability motor insurance portfolio since $1997$. It comprises two variables  `Date` and `UltimateCost`, and $457$ observations. Hereafeter is presented an excerpt of the data.
```{r, echo = FALSE}
itamtplcost
```
The data is available at the individual claim level, we can therefore process the data to get the aggregated version of it based on the date information. The original data is analysed so as to determine what might be a good distribution for the claim 
sizes. The inference and GOF procedures are then applied to the aggregate data, we can then  appreciate the consistency of the results with that of the first analysis.

The quantile-quantile plot of the individual claims against the exponential distribution
```{r, message = FALSE, echo = FALSE}
font_size_graph <- 16
# QUantile quantile plot checking for an exponential or Pareto distributon
italian_loss <- itamtplcost$UltimateCost
itamtplcost_quantile <- data.frame(
  exp_quantile = sapply(seq(0.0001,1,0.0001), function(p) -log(1-p)),
  loss_quantile = sapply(seq(0.0001,1,0.0001),function(p)  quantile(italian_loss, p)),
  log_loss_quantile = sapply(seq(0.0001,1,0.0001),function(p)  quantile(log(italian_loss) , p))
)

# Quantil-quantile plot exponential distribution
exp_qqplot <- ggplot2::ggplot(data = itamtplcost_quantile) + geom_point(mapping = aes(x = exp_quantile, y = loss_quantile)) + xlab('Standard exponential quantiles') + ylab('Empirical Quantiles') + theme_bw() +
  theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
exp_qqplot
```
exhibits a linear trend for the lower level quantiles, the fit does not look adequate in the right tail of the data.
```{r, echo = FALSE, message = FALSE, eval = FALSE}
ggsave(paste0(export_path, "QQPlot_exponential.pdf"), exp_qqplot)
```
The quantile-quantile plot of the log losses against the exponential distribution shows a linear trend for the upper level quantiles
```{r, echo = FALSE}
# Quantil-quantile plot exponential distribution
Pareto_qqplot <- ggplot2::ggplot(data = itamtplcost_quantile) + geom_point(mapping = aes(x = exp_quantile, y = log_loss_quantile)) + xlab('Standard exponential quantiles') + ylab('Empirical Quantiles') + theme_bw() + 
  theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
Pareto_qqplot
```
which means that a splicing model combining a light tailed distribution for the belly and a heavier tailed distribution for the right tail of the data might be a good idea. 
```{r, echo = FALSE, message = FALSE, eval = FALSE}
ggsave(paste0(export_path, "QQPlot_Pareto.pdf"), Pareto_qqplot)
```
This also implies a probable rejection of the compound models to be tested. The analysis is then conducted over the whole data set and on a subset made of the smaller claims. The claims that are lower than a threshold are considered to be small. The cut-off point is the upper order statistic that minimizes the asymptotic mean squared error of the Hill estimator. The mean excess plot and the Hill plot of the data are given below 
```{r, echo = FALSE, message = FALSE}
n <- length(italian_loss)
italian_loss_sorted <- sort(italian_loss, decreasing = FALSE)
#Definition of a threshold based on the tail index estimator 

Hill_amse_italian <- dAMSE(italian_loss_sorted)
# Hill_amse_italian <- dAMSE(italian_loss_sorted)
mean_excess_data <- data.frame(order_stat = italian_loss_sorted[-n],
           excess_mean = sapply(italian_loss_sorted[-n], 
            function(t) mean(italian_loss[italian_loss>t]) - t) 
           )

mean_exess_plot <- ggplot2::ggplot(data = mean_excess_data) + geom_point(mapping = aes(x = order_stat, y = excess_mean)) + xlab('Order statistic') + ylab('Mean over threshold') + geom_vline(xintercept = Hill_amse_italian$threshold) +
   scale_y_continuous(labels=function(n){format(n, scientific = TRUE)}) + theme_bw() + theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
  
mean_exess_plot

Hill_data <- data.frame(index_order_stat = 1:(n - 1),
                       Hill_est = sapply(1:(n - 1), function(k) mean(sapply(1:k, function(j) 
  j * log(italian_loss_sorted[n - j + 1] / italian_loss_sorted[n - j]))))
)
Hill_plot <- ggplot2::ggplot(data = Hill_data) + geom_point(mapping = aes(x = index_order_stat, y = Hill_est)) + xlab('Index order statistic') + ylab('Tail index') + geom_vline(xintercept = Hill_amse_italian$k0) + theme_bw() +  theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
Hill_plot
```
```{r, echo = FALSE, message = FALSE, eval = FALSE}
ggsave(paste0(export_path, "mean_exess_plot.pdf"), mean_exess_plot)
ggsave(paste0(export_path, "Hill_plot.pdf"), Hill_plot)
```
The horizontal line provide the cut-of point, the threshold is given in mean excess plot while the index of the corresponding order statistics may be viewed on the Hill estimator plot. Some descriptive statistics of the data are provided thereafter
```{r, echo = FALSE, message = FALSE, warning = FALSE}
#Summary statistics, standard deviation and kutorsis in the datasets, spike graph
U <- sort(itamtplcost$UltimateCost)
## List of descriptive statistics
list_stat <- c('No of observations', 'E(U)', 'St.Dev(U)', 'Skewness(U)', 'Kurtosis(U)', 'Minimum', 'Maximum', 'Q1', 'median', 'Q3')
## Overall statisitics
stat_U <- c(length(U), mean(U), sd(U),skewness(U), kurtosis(U), min(U), max(U), quantile(U, 0.25),quantile(U, 0.5), 
  quantile(U, 0.75))
## Statistics over the small claims
itamtplcost_small <- itamtplcost[itamtplcost$UltimateCost < Hill_amse_italian$threshold, ]
U <- itamtplcost_small$UltimateCost 
stat_U_small <- c(length(U), mean(U), sd(U),skewness(U), kurtosis(U), min(U), max(U), quantile(U, 0.25),quantile(U, 0.5), 
  quantile(U, 0.75))
stat_desc <- data.frame(Statitistics = list_stat, overall = stat_U, small_claims = stat_U_small)
stat_desc
```
We note the swift decrease of variance when considering the small claims solely. The quartiles are stable while the mean in the small claims subset decreases to get closer to the median. Table \ref{tab:EstimatedParameters} reports the method of moments estimators of the parameters of the exponential and gamma distribution.
```{r, echo = FALSE, eval = FALSE}
print(xtable(stat_desc), 
      include.rownames = FALSE, include.colnames = TRUE)
```
We will first assess the adequacy of the claim sizes data to the claim sizes distribution under $H_0$ including 

- exponential
- gamma
- inverse Gaussian

```{r, echo = FALSE, message = FALSE}
library(fitdistrplus)
small_italian_loss <- itamtplcost_small$UltimateCost 
### Large claims
fit_exp_italian <- fitdist(italian_loss, dexp, method=c("mme"))
scale_exp_italian <- 1 / fit_exp_italian$estimate
fit_gamma_italian <- fitdist(italian_loss, dgamma, method=c("mme"))
shape_gamma_italian <- fit_gamma_italian$estimate[1]
scale_gamma_italian <- 1/fit_gamma_italian$estimate[2]
fit_ingauss_italian <- c(mean(italian_loss), var(italian_loss)/mean(italian_loss)^3)

### Small claims
fit_exp_italian_small <- fitdist(small_italian_loss, dexp, method=c("mme"))
scale_exp_italian_small <- 1 / fit_exp_italian_small$estimate
fit_gamma_italian_small <- fitdist(small_italian_loss, dgamma, method=c("mme"))
shape_gamma_italian_small <- fit_gamma_italian_small$estimate[1]
scale_gamma_italian_small <- 1/fit_gamma_italian_small$estimate[2]
fit_ingauss_italian_small <- c(mean(small_italian_loss), var(small_italian_loss)/mean(small_italian_loss)^3)
### Output
Claim_sizes_parameter_estimate <- data.frame(
  parameters = c('scale.exp', 'shape.gamma', 'scale.gamma', "mean.invgauss", "dispersion.invgauss"),
  estimates = c(scale_exp_italian, shape_gamma_italian, scale_gamma_italian, fit_ingauss_italian[1], fit_ingauss_italian[2]),
  estimates_small = c(scale_exp_italian_small, shape_gamma_italian_small, scale_gamma_italian_small,fit_ingauss_italian_small[1], fit_ingauss_italian_small[2]))
Claim_sizes_parameter_estimate
```
```{r, echo = FALSE, message = FALSE, eval = FALSE}
print(xtable(Claim_sizes_parameter_estimate), 
      include.rownames = FALSE, include.colnames = TRUE)
```

We plot the histogram of the data and superimpose the density functions of the exponential, gamma and inverse Gaussian distribution on top of it. 
```{r, echo = FALSE, message = FALSE, warning = FALSE}
# Histogram over all the claims
exp_pdf <- function(x) exp(-x / scale_exp_italian) / scale_exp_italian
gamma_pdf <- function(x) dgamma(x, shape = shape_gamma_italian ,scale = scale_gamma_italian)
invgauss_pdf <- function(x) actuar::dinvgauss(x, mean = fit_ingauss_italian[1], dispersion = fit_ingauss_italian[2])
italian_loss_data <- data.frame(loss = italian_loss)
hist_italian_loss <- ggplot2::ggplot(data = italian_loss_data) + geom_histogram(mapping = aes(x = loss, y = ..density..), bg = 'lightgrey') + xlab('Density') + ylab('Claim amounts') + stat_function(fun = exp_pdf, linetype="solid") +
  stat_function(fun = gamma_pdf, linetype="dotted") +
  stat_function(fun = invgauss_pdf, linetype="dashed") +
  theme_bw() +
  theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
hist_italian_loss
                                                           
# Histogram for the small claims
exp_pdf <- function(x) exp(-x / scale_exp_italian_small) / scale_exp_italian_small
gamma_pdf <- function(x) dgamma(x, shape = shape_gamma_italian_small ,scale = scale_gamma_italian_small)
invgauss_pdf <- function(x) actuar::dinvgauss(x, mean = fit_ingauss_italian_small[1], dispersion = fit_ingauss_italian_small[2])
small_italian_loss_data <- data.frame(loss = small_italian_loss)
hist_small_italian_loss <- ggplot2::ggplot(data = small_italian_loss_data) + geom_histogram(mapping = aes(x = loss, y = ..density..), bg = 'lightgrey') + xlab('Density') + ylab('Claim amounts') + stat_function(fun = exp_pdf, linetype="solid") +
  stat_function(fun = gamma_pdf, linetype="dotted") +
  stat_function(fun = invgauss_pdf, linetype="dashed") +
  theme_bw() +
  theme(axis.title.x = element_text(size = font_size_graph),
        axis.title.y = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph)
        )
hist_small_italian_loss
```
```{r, echo = FALSE, message = FALSE, eval = FALSE}
ggsave(paste0(export_path, "hist_overall.pdf"), hist_italian_loss)
ggsave(paste0(export_path, "hist_small_claims.pdf"), hist_small_italian_loss)
```
Now we assess the fit using goodneess of fit test and Akaike criteria on all the claims
```{r, echo = FALSE, message = FALSE, warning = FALSE}
### Function to calculate KS distance, Cvm criterium and AIC for inverse Gaussian
#' fit_gof_IG function to fit and assess the fit of the Inverse Gaussian
#'
#' @param X_data sample of claim sizes 
#'
#' @return The parameters estimated via MME, the AIC, the KS ditance and the CvM distance
#' @export
#'
#' @examples
fit_gof_IG <- function(X_data){
  
  n <- length(X_data)
  params <- list(mean(X_data), var(X_data)/mean(X_data)^3)
  names(params) <- c("mean", "dispersion")
  log_L <- log(dinvgauss(X_data, mean = params$mean, dispersion = params$dispersion))
  AIC <- 2 * length(params) - 2 * sum(log_L * is.finite(log_L), na.rm = T)
  cdf_OS <- pinvgauss(sort(X_data), mean = params$mean, dispersion = params$dispersion)
  CvM <- 1 / 12 / n + sum((cdf_OS - (2 * (1:n) - 1) / 2 / n)^2)
  KS <-max(c(max((1:n) /n - cdf_OS), max(cdf_OS - (1:n - 1) / n)))
  res <- list(params, AIC, CvM, KS)
  names(res) <-  list('params', 'AIC', 'CvM', 'KS')
  return(res)
}
## AIC and Goodness of fit test
### Large claims
gof <- gofstat(list(fit_exp_italian, fit_gamma_italian), discrete = FALSE, 
               fitnames = c("exponential","gamma"))
gof_IG <- fit_gof_IG(italian_loss)
n <- length(italian_loss)
#### Parametric bootstrap
n_loop <- 100
gof_boot <- matrix(1, n_loop, 6)
for(k in 1:n_loop){
  exp_boot <- rexp(n, rate = 1 / scale_exp_italian )
  gamma_boot <- rgamma(n, shape = shape_gamma_italian, scale = scale_gamma_italian)
  invgauss_boot <- rinvgauss(n, mean = gof_IG$params$mean, dispersion = gof_IG$params$dispersion)
  fit_exp_boot <- fitdist(exp_boot, dexp, method = c("mme"))
  fit_gamma_boot <- fitdist(gamma_boot, dgamma, method = c("mme"))
  gof_invgauss_boot <- fit_gof_IG(invgauss_boot)
  gof_boot_exp <- gofstat(fit_exp_boot, discrete = FALSE, fitnames = c("exponential"))
  gof_boot_gamma <- gofstat(fit_gamma_boot, discrete = FALSE, fitnames = c("gamma"))
  gof_boot[k,] <-c(gof_boot_exp$ks, gof_boot_exp$cvm, gof_boot_gamma$ks , gof_boot_gamma$cvm, gof_invgauss_boot$KS, gof_invgauss_boot$CvM) 
}
gof_italian <- data.frame(model = c('exponential','gamma', 'invgauss'),
                         AIC = c(gof$aic, gof_IG$AIC),
                         ks = c(gof$ks, gof_IG$KS), 
                         ks_critical = c(quantile(gof_boot[,1],0.95), quantile(gof_boot[,3],0.95), quantile(gof_boot[,5],0.95)),
                         cvm = c(gof$cvm, gof_IG$CvM), 
                         cvm_critical = c(quantile(gof_boot[,2],0.95), quantile(gof_boot[,4],0.95), quantile(gof_boot[,6],0.95))  
) 
row.names(gof_italian) <- NULL
gof_italian

# print(xtable(gof_italian), 
#       include.rownames = FALSE, include.colnames = TRUE)
```
and then on the small claims
```{r, echo = FALSE, message = FALSE, warning=FALSE}
## AIC and Goodness of fit test
### Small claims
gof_small <- gofstat(list(fit_exp_italian_small, fit_gamma_italian_small), discrete = FALSE, 
               fitnames = c("exponential","gamma"))
gof_IG_small <- fit_gof_IG(small_italian_loss)
n <- length(small_italian_loss)
#### Parametric bootstrap
n_loop <- 100
gof_boot_small <- matrix(1, n_loop, 6)
for(k in 1:n_loop){
  exp_boot_small <- rexp(n, rate = 1 / scale_exp_italian_small )
  gamma_boot_small <- rgamma(n, shape = shape_gamma_italian_small, scale = scale_gamma_italian_small)
  invgauss_boot_small <- rinvgauss(n, mean = gof_IG_small$params$mean, dispersion = gof_IG_small$params$dispersion)
  fit_exp_boot_small <- fitdist(exp_boot, dexp, method = c("mme"))
  fit_gamma_boot_small <- fitdist(gamma_boot, dgamma, method = c("mme"))
  gof_invgauss_boot_small <- fit_gof_IG(invgauss_boot_small)
  gof_boot_exp_small <- gofstat(fit_exp_boot, discrete = FALSE, fitnames = c("exponential"))
  gof_boot_gamma_small <- gofstat(fit_gamma_boot, discrete = FALSE, fitnames = c("gamma"))
  gof_boot_small[k,] <-c(gof_boot_exp_small$ks, gof_boot_exp_small$cvm, gof_boot_gamma_small$ks , gof_boot_gamma_small$cvm, gof_invgauss_boot_small$KS, gof_invgauss_boot_small$CvM) 
}
gof_italian_small <- data.frame(model = c('exponential','gamma', 'invgauss'),
                         AIC = c(gof_small$aic, gof_IG_small$AIC),
                         ks = c(gof_small$ks, gof_IG_small$KS), 
                         ks_critical = c(quantile(gof_boot_small[,1],0.95), quantile(gof_boot_small[,3],0.95), quantile(gof_boot_small[,5],0.95)),
                         cvm = c(gof_small$cvm, gof_IG_small$CvM), 
                         cvm_critical = c(quantile(gof_boot_small[,2],0.95), quantile(gof_boot_small[,4],0.95), quantile(gof_boot_small[,6],0.95))  
)
row.names(gof_italian_small) <- NULL
gof_italian_small
# print(xtable(gof_italian_small), 
#       include.rownames = FALSE, include.colnames = TRUE)

```
The conclusion is that none of the models for the claim sizes lead to a good fit. We therefore expect the same conclusion when studying the aggregated data with our GOF techniques. Hereafter the data is processed so as to output the monthly aggregated data. 
```{r, message = FALSE, warning  = FALSE, echo = FALSE}
#_________________________________________________________________________________________________#
#Aggregate claim analysis
#_________________________________________________________________________________________________#
# Preprocessing to collect claim sizes aggregated monthly
itamtplcost <- data.frame(itamtplcost, mm_yy = substr(itamtplcost$Date,4,10), 
                          yyyy = substr(itamtplcost$Date,7,10))
itamtplcost_small <- itamtplcost_small[itamtplcost$UltimateCost < Hill_amse_italian$threshold,] 
itamtplcost_small <- data.frame(itamtplcost_small, 
                                        mm_yy = substr(itamtplcost_small$Date,4,10), 
                                        yyyy = substr(itamtplcost_small$Date,7,10))

date <- {}
claim_frequency <- {}
claim_frequency_small <- {}
total_claim_size <- {}
total_claim_size_small <- {}
i <- 0
for(y in 1997:2012){
  for(m in 1:12){
    i <- i +1
    if(m < 10){
      date[i] <- paste(0, m, "/", y, sep = '')
      }
    else{
      date[i] <- paste(m, "/", y, sep = '')
      }
    claim_frequency[i] <- length(itamtplcost$mm_yy[paste(itamtplcost$mm_yy) == date[i]])
    claim_frequency_small[i] <- length(itamtplcost_small$mm_yy[paste(itamtplcost_small$mm_yy) == date[i]])
    if(claim_frequency[i] == 0){
      total_claim_size[i] <- 0
    }
    else{
      total_claim_size[i] <- sum(itamtplcost$UltimateCost[paste(itamtplcost$mm_yy) == date[i]])
    }
    if(claim_frequency_small[i] == 0){
      total_claim_size_small[i] <- 0
    }
    else{
      total_claim_size_small[i] <- sum(itamtplcost_small$UltimateCost[paste(itamtplcost_small$mm_yy) == date[i]])
    }
  }
}
itamtplcost_monthly <- data.frame(mm_yy = date, claim_frequency = claim_frequency, total_claim_size <- total_claim_size)
itamtplcost_small_monthly <- data.frame(mm_yy = date, claim_frequency = claim_frequency_small, total_claim_size <- total_claim_size_small)
### Output Table
itamtplcost_monthly[1:5,]
# print(xtable(itamtplcost_monthly[1:5,]), 
#       include.rownames = FALSE,include.colnames = TRUE)
```
Now we turn to the study of the claim frequency distribution. We fit and assess the adequacy of the Poisson and geometric distribution to the claim count data. 
```{r, message = FALSE, warning = FALSE, echo = FALSE}
# Goodness of fit of the claim frequency distributions
fpois <- fitdist(itamtplcost_monthly$claim_frequency, "pois")
fgeom <- fitdist(itamtplcost_monthly$claim_frequency, "geom")
fnbinom <- fitdist(itamtplcost_monthly$claim_frequency, "nbinom")
fpois_small <- fitdist(itamtplcost_small_monthly$claim_frequency, "pois")
fgeom_small <- fitdist(itamtplcost_small_monthly$claim_frequency, "geom")
fnbinom_small <- fitdist(itamtplcost_small_monthly$claim_frequency, "nbinom")

# gof_claim_frequency <- gofstat(list(fpois, fgeom, fnbinom) , discrete = TRUE, 
#                                fitnames = c("Poisson","Geometric","Negative-Binomial"))
# gof_claim_frequency_small <- gofstat(list(fpois_small, fgeom_small, fnbinom_small) , discrete = TRUE, 
gof_claim_frequency <- gofstat(list(fpois, fgeom) , discrete = TRUE,
                               fitnames = c("Poisson","Geometric"))
gof_claim_frequency_small <- gofstat(list(fpois_small, fgeom_small) , discrete = TRUE,
fitnames = c("Poisson","Geometric")) 

### Output
claim_count_summary <- data.frame(model = c("Poisson", "geometric", "Poisson", "geometric"),
             estimated.parameters = c(fpois$estimate, fgeom$estimate, fpois_small$estimate, fgeom_small$estimate),
             Chisq = c(gof_claim_frequency$chisq, gof_claim_frequency_small$chisq),
             AIC = c(gof_claim_frequency$aic, gof_claim_frequency_small$aic)
             )

print(xtable(claim_count_summary
  , include.rownames = FALSE,include.colnames = TRUE))
claim_count_summary
```
The aggregated claim sizes data is fit using 6 different models including 

- Poisson-exponential
- Poisson-gamma
- Poisson-inverse Gaussian
- Geometric-exponential
- Geometric-gamma
- Geometric-inverse Gaussian

```{r, message = FALSE, warning = FALSE, echo = FALSE}
# Inference of the compound distribution
## Large claims
geom_exp <- MME_CD(itamtplcost_monthly$total_claim_size, 'geom', 'exp', 'partial-MME')
geom_gamma <- MME_CD(itamtplcost_monthly$total_claim_size, 'geom', 'gamma', 'partial-MME')
geom_invgauss <- MME_CD(itamtplcost_monthly$total_claim_size, 'geom', 'invgauss', 'partial-MME')
poisson_exp <- MME_CD(itamtplcost_monthly$total_claim_size, 'pois', 'exp', 'partial-MME')
poisson_gamma <- MME_CD(itamtplcost_monthly$total_claim_size, 'pois', 'gamma', 'partial-MME')
poisson_invgauss <- MME_CD(itamtplcost_monthly$total_claim_size, 'pois', 'invgauss', 'partial-MME')

## Small claims
geom_exp_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'geom', 'exp', 'partial-MME')
geom_gamma_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'geom', 'gamma', 'partial-MME')
geom_invgauss_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'geom', 'invgauss', 'partial-MME')
poisson_exp_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'pois', 'exp', 'partial-MME')
poisson_gamma_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'pois', 'gamma', 'partial-MME')
poisson_invgauss_small <- MME_CD(itamtplcost_small_monthly$total_claim_size, 'pois', 'invgauss', 'partial-MME')

## Output Table 
params_CD <- data.frame(model = c(rep("Poisson-exponential",2), rep("Poisson-gamma",3), rep("Poisson-invgauss", 3), 
                       rep("geometric-exponential", 2)), 
             parameters = c(poisson_exp[c(2, 4)], poisson_gamma[2:4], poisson_invgauss[2:4], geom_exp[c(1,4)]), 
             parameter_small = c(poisson_exp_small[c(2, 4)], poisson_gamma_small[2:4], poisson_invgauss_small[2:4], 
                                 geom_exp_small[c(1,4)])
  )

print(xtable(params_CD, include.rownames = FALSE,include.colnames = TRUE))
params_CD
```
The method of moment results in negative values of the parameter within the geometric-gamma and geometric-inverse Gaussian that are therefore discarded in the remainder of this study. We now apply our goodness-of-fit procedure staring with distribution based ones on all the claims
```{r, message = FALSE, echo = FALSE, warning = FALSE}
#All claims
B = 100
## KS test 
ks_geom_exp <- ks_gof(itamtplcost_monthly$total_claim_size, 'geom', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_exp <- ks_gof(itamtplcost_monthly$total_claim_size, 'pois', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_gamma <- ks_gof(itamtplcost_monthly$total_claim_size, 'pois', 'gamma', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_invgauss <- ks_gof(itamtplcost_monthly$total_claim_size, 'pois', 'invgauss', 35,
                   'truncation', B, method = 'partial-MME')
## CvM test
cvm_geom_exp <- cvm_gof(itamtplcost_monthly$total_claim_size, 'geom', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_exp <- cvm_gof(itamtplcost_monthly$total_claim_size, 'pois', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_gamma <- cvm_gof(itamtplcost_monthly$total_claim_size, 'pois', 'gamma', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_invgauss <- cvm_gof(itamtplcost_monthly$total_claim_size, 'pois', 'invgauss', 35,
                   'truncation', B, method = 'partial-MME')
df_test_all_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             KS = c(ks_geom_exp[1], ks_pois_exp[1], ks_pois_gamma[1], ks_pois_invgauss[1]),
             KS_critical =  c(ks_geom_exp[2], ks_pois_exp[2], ks_pois_gamma[2], ks_pois_invgauss[2]),
             CvM = c(cvm_geom_exp[1], cvm_pois_exp[1], cvm_pois_gamma[1], cvm_pois_invgauss[1]),
             CvM_critical = c(cvm_geom_exp[2], cvm_pois_exp[2], cvm_pois_gamma[2], cvm_pois_invgauss[2]))
##Latex table
# print(xtable(df_test_all_claims
#   , digits= -2), 
#   include.rownames = FALSE,include.colnames = TRUE)
##output table
df_test_all_claims
```
then on the small claims
```{r, message = FALSE, warning = FALSE, echo = FALSE}
#Small claims
## KS test 
ks_geom_exp_small <- ks_gof(itamtplcost_small_monthly$total_claim_size, 'geom', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_exp_small <- ks_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_gamma_small <- ks_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'gamma', 35,
                   'truncation', B, method = 'partial-MME')
ks_pois_invgauss_small <- ks_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'invgauss', 35,
                   'truncation', B, method = 'partial-MME')
## CvM test
cvm_geom_exp_small <- cvm_gof(itamtplcost_small_monthly$total_claim_size, 'geom', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_exp_small <- cvm_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'exp', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_gamma_small <- cvm_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'gamma', 35,
                   'truncation', B, method = 'partial-MME')
cvm_pois_invgauss_small <- cvm_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'invgauss', 35,
                   'truncation', B, method = 'partial-MME')
df_test_small_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             KS = c(ks_geom_exp_small[1], ks_pois_exp_small[1], ks_pois_gamma_small[1], ks_pois_invgauss_small[1]),
             KS_critical =  c(ks_geom_exp_small[2], ks_pois_exp_small[2], ks_pois_gamma_small[2], ks_pois_invgauss_small[2]),
             CvM = c(cvm_geom_exp_small[1], cvm_pois_exp_small[1], cvm_pois_gamma_small[1], cvm_pois_invgauss_small[1]),
             CvM_critical = c(cvm_geom_exp_small[2], cvm_pois_exp_small[2], cvm_pois_gamma_small[2], cvm_pois_invgauss_small[2]))
##Latex table
# print(xtable(df_test_small_claims
#   , digits= -2), 
#   include.rownames = FALSE,include.colnames = TRUE)
##output table
df_test_small_claims
```
We turn to the Laplace transform based techniques using the $\text{SE}_n(t)$ distance on all the claims

```{r, message = FALSE, warning = FALSE, echo = FALSE}
#L2 distance
beta_vec <- c(10^(-3), 10^(-2))
B = 100
## All Claims
L2_geom_exp <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_monthly$total_claim_size, 'geom', 'exp', beta, B, method = 'partial-MME', T))
L2_poisson_exp <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_monthly$total_claim_size, 'pois', 'exp', beta, B, method = 'partial-MME', T))
L2_poisson_gamma <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_monthly$total_claim_size, 'pois', 'gamma', beta, B, method = 'partial-MME', T))
L2_poisson_invgauss <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_monthly$total_claim_size, 'pois', 'invgauss', beta, B, method = 'partial-MME', T))

lt_L2_test_all_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             beta_3 = c(L2_geom_exp[1, 1], L2_poisson_exp[1, 1], L2_poisson_gamma[1, 1], L2_poisson_invgauss[1, 1]),
             beta_3_critical =  c(L2_geom_exp[2, 1], L2_poisson_exp[2, 1], L2_poisson_gamma[2, 1], L2_poisson_invgauss[2, 1]),
             beta_2 = c(L2_geom_exp[1, 2], L2_poisson_exp[1, 2], L2_poisson_gamma[1, 2], L2_poisson_invgauss[1, 2]),
             beta_2_critical =  c(L2_geom_exp[2, 2], L2_poisson_exp[2, 2], L2_poisson_gamma[2, 2], L2_poisson_invgauss[2, 2]))
##Latex table
# print(xtable(lt_L2_test_all_claims
#   , digits= -2), 
#   include.rownames = FALSE, include.colnames = TRUE)
##output table
lt_L2_test_all_claims
```

and small claims

```{r, message = FALSE, warning = FALSE, echo = FALSE, eval = FALSE}
## Small Claims
L2_geom_exp_small <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_small_monthly$total_claim_size, 'geom', 'exp', beta, B, method = 'partial-MME', T))
L2_poisson_exp_small <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'exp', beta, B, method = 'partial-MME', T))
L2_poisson_gamma_small <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'gamma', beta, B, method = 'partial-MME', T))
L2_poisson_invgauss_small <- sapply(beta_vec, function(beta) lt_L2_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'invgauss', beta, B, method = 'partial-MME', T))

lt_L2_test_small_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             beta_3 = c(L2_geom_exp_small[1, 1], L2_poisson_exp_small[1, 1], L2_poisson_gamma_small[1, 1], L2_poisson_invgauss_small[1, 1]),
             beta_3_critical =  c(L2_geom_exp_small[2, 1], L2_poisson_exp_small[2, 1], L2_poisson_gamma_small[2, 1], L2_poisson_invgauss_small[2, 1]),
             beta_2 = c(L2_geom_exp_small[1, 2], L2_poisson_exp_small[1, 2], L2_poisson_gamma_small[1, 2], L2_poisson_invgauss_small[1, 2]),
             beta_2_critical =  c(L2_geom_exp_small[2, 2], L2_poisson_exp_small[2, 2], L2_poisson_gamma_small[2, 2], L2_poisson_invgauss_small[2, 2]))
##Latex table
# print(xtable(lt_L2_test_small_claims
#   , digits= -2), 
#   include.rownames = FALSE,include.colnames = TRUE)
##output table
lt_L2_test_small_claims
```

Finally the Laplace transform based techniques using the $\text{DE}_n(t)$ distance on all the claims 

```{r, message = FALSE, warning = FALSE, echo = FALSE}
#ODE distance
beta_vec <- c(10^(-1), 1)
B = 100
## All Claims
ODE_geom_exp <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_monthly$total_claim_size, 'geom', 'exp', beta, B, method = 'partial-MME', T))
ODE_poisson_exp <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_monthly$total_claim_size, 'pois', 'exp', beta, B, method = 'partial-MME', T))
ODE_poisson_gamma <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_monthly$total_claim_size, 'pois', 'gamma', beta, B, method = 'partial-MME', T))
ODE_poisson_invgauss <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_monthly$total_claim_size, 'pois', 'invgauss', beta, B, method = 'partial-MME', T))

lt_ODE_test_all_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             beta_0.1 = c(ODE_geom_exp[1, 1], ODE_poisson_exp[1, 1], ODE_poisson_gamma[1, 1], ODE_poisson_invgauss[1, 1]),
             beta_0.1_critical =  c(ODE_geom_exp[2, 1], ODE_poisson_exp[2, 1], ODE_poisson_gamma[2, 1], ODE_poisson_invgauss[2, 1]),
             beta_1 = c(ODE_geom_exp[1, 2], ODE_poisson_exp[1, 2], ODE_poisson_gamma[1, 2], ODE_poisson_invgauss[1, 2]),
             beta_1_critical =  c(ODE_geom_exp[2, 2], ODE_poisson_exp[2, 2], ODE_poisson_gamma[2, 2], ODE_poisson_invgauss[2, 2]))
##Latex table
# print(xtable(lt_ODE_test_all_claims
#   , digits= -2), 
#   include.rownames = FALSE,include.colnames = TRUE)
##output table
lt_ODE_test_all_claims
```
and on the small claims
```{r, message = FALSE, warning = FALSE,echo = FALSE}
## Small Claims
ODE_geom_exp_small <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_small_monthly$total_claim_size, 'geom', 'exp', beta, B, method = 'partial-MME', T))
ODE_poisson_exp_small <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'exp', beta, B, method = 'partial-MME', T))
ODE_poisson_gamma_small <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'gamma', beta, B, method = 'partial-MME', T))
ODE_poisson_invgauss_small <- sapply(beta_vec, function(beta) lt_ODE_gof(itamtplcost_small_monthly$total_claim_size, 'pois', 'invgauss', beta, B, method = 'partial-MME', T))

lt_ODE_test_small_claims <- data.frame(model = c('geometric-exp', 'poisson-exp', 'poisson-gamma', 'Poisson-inverse Gaussian'),
             beta_0.1 = c(ODE_geom_exp_small[1, 1], ODE_poisson_exp_small[1, 1], ODE_poisson_gamma_small[1, 1], ODE_poisson_invgauss_small[1, 1]),
             beta_0.1_critical =  c(ODE_geom_exp_small[2, 1], ODE_poisson_exp_small[2, 1], ODE_poisson_gamma_small[2, 1], ODE_poisson_invgauss_small[2, 1]),
             beta_1 = c(ODE_geom_exp_small[1, 2], ODE_poisson_exp_small[1, 2], ODE_poisson_gamma_small[1, 2], ODE_poisson_invgauss_small[1, 2]),
             beta_1_critical =  c(ODE_geom_exp_small[2, 2], ODE_poisson_exp_small[2, 2], ODE_poisson_gamma_small[2, 2], ODE_poisson_invgauss_small[2, 2]))
##Latex table
# print(xtable(lt_ODE_test_small_claims
#   , digits= -2), 
#   include.rownames = FALSE,include.colnames = TRUE)
##output table
lt_ODE_test_small_claims

```

