---
title: "Monte Carlo study to calibrate the parameter in the weight function"
author: "Pierre-O Goffard"
output:
  html_document:
    df_print: paged
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(FTCD)
library(rmarkdown)
library(latex2exp)
library(knitr)
```
The goal of this notebook is determine an acceptable value for the parameter in the exponential weight function used with the Laplace transform based goodness-of-fit test. The study is conducted when testing for a compound Poisson-exponential model under $H_0$ to fit the aggregated claim amounts that will actually come from a compound Poisson-Gamma model. The level and the power of the test the Laplace transform based GOF test are computed for both the $\text{SE}_n^{2}$ and $\text{DE}_n(t)$ distance for values of $\beta$ ranging in the set $\{10^{-13},10^{-12}, \ldots, 10^3\}$. The evaluation is performed using a parametric bootstrap routine combined to the Warp speed method with $10,000$ samples generated. The following chunk allows us to collect the simulation data and should be run using some distant computing server. 
```{r, eval = FALSE, include = FALSE}
# inference_methods <- c("MME", "partial-MME")
# methods <- c("LT_L2", "LT_ODE")
# rvec <- c(0.5, 0.75, 1, 2, 4)
# MC <- 10000
# beta_vec <- 10^seq(-13 , 3, 1)
# res <- NULL
# 
# for(method in methods){
#   print(method)
#   for(r in rvec){
#     print(r)
#     for(inference_method in inference_methods){
#       print(inference_method)
#       eval(
#         parse(
#           text = paste0("power_",
#                         r,
#                         "_",
#                         method,
#                         " <- data.frame(
#                         r = rep(",r,", length(beta_vec)),
#                         LT_gof_method = rep('", method,"', length(beta_vec)),
#                         Inference_method = rep('", inference_method,"', length(beta_vec)),
#                         beta = beta_vec,
#                         power = sapply(beta_vec, function(beta) p_value(100, 'pois', 'gamma',c(0, 1, ",
#                         r,
#                         ", 1), 'pois', 'exp', MC,'",
#                         inference_method,
#                         "', '",
#                         method,
#                         "', beta)))")
#         )
#       )
#       res <- rbind(res, eval(parse(text = paste0("power_",r,"_",method))))
#     }
# 
#   }
# }
# 
# write_csv(res, path = "~/Goffard-Jammalamadaka-Meintanis/Simulation_DATA_Export/Calibration_Exp_Data.txt")

#Calibration <- read.csv("~/Goffard-Jammalamadaka-Meintanis/Simulation_DATA_Export/Calibration_Exp_Data.txt")
```

We start by studying the level associated to the two tests and the two inference methods.

```{r, echo = FALSE, warning = FALSE, message = FALSE}
#PC
Calibration_data <- read.csv("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Simulation_DATA/Calibration_Exp_Data.txt")
#Mac
#Calibration_data <- read.csv("~/Dropbox/Goffard-Jammalamadaka-Meintanis/Simulation_DATA/Calibration_Exp_Data.txt")
font_size_graph <- 12
level_plot <- ggplot(data = Calibration_data %>% filter(r == "1") %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point(aes(colour = var_qual)) + geom_line(aes(colour = var_qual)) + labs(linetype = "GOF and inference method", colour = "GOF and inference method") +
  theme(axis.title = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph),
        legend.text = element_text(size = font_size_graph),
        legend.title = element_text(size = font_size_graph),
        legend.position = "bottom")
level_plot

# The plot in the paper is obtained by running the following code
# font_size_graph <- 16
# level_plot <- ggplot(data = Calibration_data %>% filter(r == "1") %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point() + geom_line() + theme_bw() + 
#   scale_linetype_manual(values=c('dotted','dashed','solid', 'dotdash')) + xlab(TeX('$\\ln(\\beta)/\\ln(10)$')) + ylab('probability of rejection') +
#   theme(axis.title = element_text(size = font_size_graph),
#         axis.text = element_text(size = font_size_graph),
#         legend.text = element_text(size = font_size_graph),
#         legend.title = element_text(size = font_size_graph),
#         legend.position = "none")
# level_plot
#ggsave("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/level_plot.pdf", plot = level_plot)
```

At a $95\%$ confidence level the p-value of test is expected to be $5\%$ when the input samples come from a Poisson-exponential distribution. This true for both of he procedure when $\beta$ is between $10^{-4}$ and $1$. We may disregard the other values of $\beta$ to study the power of the tests

```{r, echo = FALSE, warning = FALSE, message = FALSE}
library(gridExtra)
power_0.5 <- ggplot(data = Calibration_data %>% filter(r == "0.5" & beta > 10^(-7) &  beta <= 100) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point(aes(colour = var_qual)) + geom_line(aes(colour = var_qual)) + ggtitle('r = 1/2') + labs(linetype = "GOF and inference method", colour = "GOF and inference method") + theme_bw() +
  theme(axis.title = element_text(size = 8),
        axis.text = element_text(size = 8),
        title = element_text(size = 8),
        legend.text = element_text(size = 7),
        legend.title = element_text(size = 7),
        legend.position="left")

power_0.75 <- ggplot(data = Calibration_data %>% filter(r == "0.75"& beta > 10^(-7)&  beta <= 100) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point(aes(colour = var_qual)) + geom_line(aes(colour = var_qual)) + ggtitle('r = 3/4') + labs(linetype = "", colour = "") + theme_bw() +
  theme(axis.title = element_text(size = 8),
        axis.text = element_text(size = 8),
        title = element_text(size = 8),
        legend.position="none")
  
power_2 <- ggplot(data = Calibration_data %>% filter(r == "2"& beta > 10^(-7)&  beta <= 100) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point(aes(colour = var_qual)) + geom_line(aes(colour = var_qual)) + ggtitle('r = 2') + labs(linetype = "", colour = "") + theme_bw() +
  theme(axis.title = element_text(size = 8),
        axis.text = element_text(size = 8),
        title = element_text(size = 8),
        legend.position="none")

power_4 <- ggplot(data = Calibration_data %>% filter(r == "4" & beta > 10^(-7)&  beta <= 100) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point(aes(colour = var_qual)) + geom_line(aes(colour = var_qual)) + ggtitle('r = 4') + labs(linetype = "", colour = "") + theme_bw() +
  theme(axis.title = element_text(size = 8),
        axis.text = element_text(size = 8),
        title = element_text(size = 8),
        legend.position="none")

power_plot <- grid.arrange(power_0.5, power_0.75,power_2, power_4, ncol = 2, nrow = 2)
power_plot
```


```{r, echo = FALSE, message = FALSE, include = FALSE, eval = FALSE}
# The plots in the paper are obtained via the following code
font_size_graph <- 16
power_0.5 <- ggplot(data = Calibration_data %>% filter(r == "0.5") %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point() + geom_line() + theme_bw() + ylab('probability of rejection') + xlab(TeX('$\\ln(\\beta)/\\ln(10)$')) +
  scale_linetype_manual(values=c('dotted','dashed','solid', 'dotdash')) +
  theme(axis.title = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph),
        title = element_text(size = font_size_graph),
        legend.text = element_text(size = font_size_graph),
        legend.title = element_text(size = font_size_graph),
        legend.position="none")
power_0.5

ggsave("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/power_05.pdf", plot = power_0.5)

power_0.75 <- ggplot(data = Calibration_data %>% filter(r == "0.75" ) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point() + geom_line() + theme_bw() + ylab('probability of rejection') + xlab(TeX('$\\ln(\\beta)/\\ln(10)$')) +
  scale_linetype_manual(values=c('dotted','dashed','solid', 'dotdash')) +
  theme(axis.title = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph),
        title = element_text(size = font_size_graph),
        legend.text = element_text(size = font_size_graph),
        legend.title = element_text(size = font_size_graph),
        legend.position="none")
power_0.75

ggsave("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/power_075.pdf", plot = power_0.75)

power_2 <- ggplot(data = Calibration_data %>% filter(r == "2") %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point() + geom_line() + theme_bw() + ylab('probability of rejection') + xlab(TeX('$\\ln(\\beta)/\\ln(10)$')) +
  scale_linetype_manual(values=c('dotted','dashed','solid', 'dotdash')) +
  theme(axis.title = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph),
        title = element_text(size = font_size_graph),
        legend.text = element_text(size = font_size_graph),
        legend.title = element_text(size = font_size_graph),
        legend.position="none")
power_2

ggsave("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/power_2.pdf", plot = power_2)

power_4 <- ggplot(data = Calibration_data %>% filter(r == "4" ) %>% mutate(var_qual = paste(LT_gof_method,"&",Inference_method)), mapping = aes(x = log(beta) / log(10), y = power, linetype = var_qual)) + geom_point() + geom_line() + theme_bw() + ylab('probability of rejection') + xlab(TeX('$\\ln(\\beta)/\\ln(10)$')) +
  scale_linetype_manual(values=c('dotted','dashed','solid', 'dotdash')) +
  theme(axis.title = element_text(size = font_size_graph),
        axis.text = element_text(size = font_size_graph),
        title = element_text(size = font_size_graph),
        legend.text = element_text(size = font_size_graph),
        legend.title = element_text(size = font_size_graph),
        legend.position="none")
power_4

ggsave("C:/Users/pierr/Dropbox/Goffard-Jammalamadaka-Meintanis/Pictures/power_4.pdf", plot = power_4)
```



